|

### 2021-10-06 published/03-Chp-Systematic-Review.Rmd
Working version

# Systematic review of all available evidence on the association between blood lipids and dementia outcomes {#sys-rev-heading}

@@

A straight-forward random-effects meta-analysis model was employed to combine the identified results. A random-effects model was chosen due to the ...

<!-- TODO Finish this description -->

Results were stratified into subgroups on the basis of the overall risk of bias 
assessment, and summary estimates for each subgroup, in addition to an overall effect estimate, are displayed. Additional descriptive statistics are presented, while prediction intervals are shown as a dotted line around the overall effect estimate. Finally, a test subgroup differences between studies at different levels of risk of bias was performed (see subsequent Section \@ref(sys-rev-visualising-results)). All models were implemented using the `metafor` R package.

@@

@@

```{r mrAssumptions, echo = FALSE, results="asis", fig.pos = "H",fig.align='center', fig.cap='(ref:mrAssumptions-cap)', out.width='70%', fig.scap='(ref:mrAssumptions-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/mrAssumptions.png"))
```
<!----------------------------------------------------------------------------->

@@

```{r preprintGrowth, echo = FALSE, results="asis", fig.pos = "H",fig.align='center',fig.cap='(ref:preprintGrowth-cap)', out.width='80%',fig.align='center',fig.scap='(ref:preprintGrowth-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/preprint_growth.png"))
```
<!----------------------------------------------------------------------------->

>>>>

# Systematic review of all evidence available on the association between blood lipids and dementia outcomes {#sys-rev-heading}

@@

For

A random-effects meta-analysis model was employed to combine the different included studies. <!-- TODO Need more information on the difference between the two approaches, and their formula here, and description of different methods and quarrels regarding distinction fixed effect vs random effects meta-analyses. --> The fixed-effect method was implemented as:

<!-- TODO Check these against those in Ben's thesis paper -->

Results were stratified into subgroups on the basis of the overall risk of bias assessment, and summary estimates for each subgroup, in addition to an overall effect estimate, are displayed. Additional descriptive statistics are presented, while prediction intervals are shown as a dotted line around the overall effect estimate. Finally, a test subgroup differences between studies at different levels of risk of bias was performed (see subsequent Section \@ref(sys-rev-visualising-results)).

Random-effects analyses assume that differences in study design and execution mean that the study effects are normally distributed around a common treatment effect ($\mu$) with a variance of $\tau^2$

\begin{equation}
  \theta_i \sim \mathcal{N}(\mu, \tau^2) (\#eq:eq9)
\end{equation}

<!-- Random-effects methods estimate $\tau^2$ to estimate the common effect ($\mu$). There are many estimators of $\tau^2$ with varying assumptions [@Veroniki2016; @Bakbergenuly2020], the details of which are beyond the scope of this article. The estimate of $\tau^2$ is incorporated into the weighting of each study -->

\begin{equation}
  w_i = \frac{1}{v_i + \hat{\tau^2}} (\#eq:eq10)
\end{equation}

<!-- A random-effects meta-analysis allows for study-specific effects, and assumes that the true effect estimated by each study varies and is assumed to be randomly and normally distributed on the transformed scale (e.g. log-ORs) between studies, with a variance of 𝜏2. The between-study variance is estimated (usually using the “method of moments” or DerSimonian and Laird estimate), and used to modify the weights of studies when calculating the summary effect estimate and variance. The weight of each study is 1𝑣𝑖+𝜏2 where 𝑣𝑖 is the variance of the 𝑖𝑡ℎ study and 𝜏2 is the estimate of the between-study variance. So long as the between-study variance is larger than 0, smaller studies will be given more weight in random-effects meta-analysis than in a fixed-effect meta-analysis. If the between-study variance is 0, then the random-effects model is equivalent to the fixed-effect model. -->
<!-- In both fixed-effect and random-effects inverse-variance meta-analysis, the summary effect estimate and variance are estimated in the same way. The effect estimates (𝜃𝑖) from each study can be (transformed) ORs, relative risks (RRs), standardised mean differences (SMDs) or other types of estimates: -->
<!-- 𝜃̂𝑆𝑢𝑚𝑚𝑎𝑟𝑦=⁡Σ𝑤𝑖𝜃𝑖Σ𝑤𝑖 -->
<!-- (2) -->
<!-- 𝑉𝑎𝑟𝑖𝑎𝑛𝑐𝑒⁡𝑜𝑓⁡𝜃̂𝑆𝑢𝑚𝑚𝑎𝑟𝑦=⁡1Σ𝑤𝑖 -->
<!-- (3) -->
<!-- where 𝜃𝑖 is effect estimate and 𝑤𝑖 is the weight from the 𝑖𝑡ℎ study on an approximately normal scale. -->

<!-- \begin{equation} -->
<!--   \theta_i = \mu + u_i -->
<!--   (\#eq:meta-analysis-random) -->
<!-- \end{equation} -->

<!-- \begin{equation} -->
<!--   $weighted\ average = \frac{\sum Y_i (1/SE_i^2)}{\sum(1/SE_i^2)}$ -->
<!--   (\#eq:meta-analysis-fixed) -->
<!-- \end{equation} -->

<!-- where ... -->

<!-- TODO Need equation for random effects too. See Sean's thesis here. -->

@@

<!-- Will also need description of dose-response meta-analysis here, with reference to forthcoming book Julian sent on. -->

@@

```{r mrAssumptions, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:mrAssumptions-cap)', out.width='70%', fig.scap='(ref:mrAssumptions-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/mrAssumptions.png"))
```
<!----------------------------------------------------------------------------->

@@

```{r preprintGrowth, echo = FALSE, results="asis", fig.pos = "H",fig.align='center',fig.cap='(ref:preprintGrowth-cap)', out.width='100%', fig.scap='(ref:preprintGrowth-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/preprint_growth.png"))
```
<!----------------------------------------------------------------------------->
